Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}

### 2021-03-20 inst/skeleton/ms.Rmd
move to inst/skeleton for ease of messing with things

---
title: "Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}"
thanks: "Replication files are available on the author's Github account (http://github.com/svmiller/steveproj). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com. Carl Sagan has regrettably not been with us for 25 years and this tutorial is so beneath someone of his stature."
author:
- name: Carl Sagan
  affiliation: Cornell University & the Cosmos
- name: Steven V. Miller
  affiliation: Clemson University
# bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`" # This would be more general
bibliography: inst/refs.bib
abstract: "Gathered by gravity rings of Uranus finite but unbounded extraordinary claims require extraordinary evidence permanence of the stars white dwarf. A mote of dust suspended in a sunbeam invent the universe rich in heavy atoms hearts of the stars vastness is bearable only through love at the edge of forever. Something incredible is waiting to be known descended from astronomers bits of moving fluff vanquish the impossible with pretty stories for which there's little good evidence a very small stage in a vast cosmic arena and billions upon billions upon billions upon billions upon billions upon billions upon billions."
keywords: "R Markdown, R, Make, {stevetemplates}, the Cosmos, billions and billions"
geometry: margin=1in
mainfont: cochineal
#sansfont: Linux Biolinum O
fontsize: 11pt
endnote: no
# pandocparas: TRUE
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
header-includes:
  - \usepackage{longtable}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
---

>>>>

---
title: "Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}"
thanks: "Replication files are available on the author's Github account (http://github.com/svmiller/steveproj). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com. Carl Sagan has regrettably not been with us for 25 years and this tutorial is so beneath someone of his stature."
author:
- name: Carl Sagan
  affiliation: Cornell University & the Cosmos
- name: Steven V. Miller
  affiliation: Clemson University
# bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`" # This would be more general
bibliography: inst/refs.bib
abstract: "Gathered by gravity rings of Uranus finite but unbounded extraordinary claims require extraordinary evidence permanence of the stars white dwarf. A mote of dust suspended in a sunbeam invent the universe rich in heavy atoms hearts of the stars vastness is bearable only through love at the edge of forever. Something incredible is waiting to be known descended from astronomers bits of moving fluff vanquish the impossible with pretty stories for which there's little good evidence a very small stage in a vast cosmic arena and billions upon billions upon billions upon billions upon billions upon billions upon billions."
keywords: "R Markdown, R, Make, {stevetemplates}, the Cosmos, billions and billions"
geometry: margin=1in
mainfont: cochineal
#sansfont: Linux Biolinum O
fontsize: 11pt
endnote: no
# pandocparas: TRUE
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
  removetitleabstract: ""
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
removetitleabstract: "`r params$removetitleabstract`"
header-includes:
  - \usepackage{longtable}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
---
